A Database Management System for a Geospatially-Enabled Interactive Game

### 2018-12-11 paper/MSDS7330DBMSforGeospatiallyEnabledGame.tex
Aligned Some List Formatting

\begin{enumerate}
  \item Client-side application. We decided to support 2 major platforms that got widespread adoption: Android and iOS. For the proof-of-concept we focused on iOS. 
  \item Backend services, or middle layer. This component performs server-side operations, enforces gameplay rules and handles requests to our database. 
  \item Geospatially enabled database. Here all information regarding our players, objects and corresponding states is being kept. 
\end{enumerate}

>>>>

\begin{enumerate}
  \item Client-side application: We decided to support 2 major platforms that got widespread adoption: Android and iOS. For the proof-of-concept we focused on iOS. 
  \item Backend services, or middle layer: This component performs server-side operations, enforces gameplay rules and handles requests to our database. 
  \item Geospatially enabled database: Here all information regarding our players, objects and corresponding states is being kept. 
\end{enumerate}
